### 2020-10-24 thesis/msc-thesis.tex
minor changes

@@

One possibility for adding DCSS capabilities is the usage of solutions from DCSS providers. They keep companies and organizations up to date
with DCSS requirements and help with integration. Another possibility is the usage of websites and applications developed in self-work.

\chapter{Objectives}

@@

The objective of this bachelor thesis is to improve the capability of enterprises and organizations to integrate DCSS providers \hl{(or solutions?)}.
The thesis explains the basis of what DCSS and its providers are, which relevant scenarios exist and how DCSS providers can help
in the digital transformation.

@@

Based on DCSS scenarios resulting from governmental regulations (due to their current relevance), an integration architecture is presented, which describes
integration of these scenarios. It provides information on which type of systems and data objects an existing
architecture requires. It models how CSS providers and system architectures can communicate -
deliver data and instructions. And it shows how, with fast development and deployment speed, integration can be applied to
heterogeneous system architectures, be non-invasive and reliable.

@@

@@

@@

\subsection{Training Promotion (BAföG)}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

@@

@@

\subsection{e-Prescription}
Reference can be found in the "Ärzteblatt" \cite{Ärzteblatt}.
\\\\
The user can have the right to manage his prescriptions via an App. Doctors give digital prescriptions to users app,
which can digitally be used in pharmacies also without physically being there.
\\\\
Regulation: "Gesetz für mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
\\\\
e-Prescription processes \cite{gematik-e-rezept}
\begin{enumerate}
     \item Doctor creates digital prescription if he has access to "Telematikinfrastruktur" and "Heilberufausweis"
     \item Prescription is saved on "Telematikinfrastruktur"
     \item Doctor displays a QR-Code (prescription-token)
     \item Patient can receive QR-Code in App (or get a printout)
     \item Patient can check availability of drug in pharmacies via the app
     \item Patient can "apply" the prescription to a pharmacy via the app
     \item prescription is now irrevocably bound to the pharmacy and gets reserved
     \item pharmacy can use prescription-token (in QR-Code) to access prescription in "Telematikinfrastruktur"
     \item pharmacy notifies patient if or when the drug is available
     \item drug can be picked up by patient or be delivered
     \item If user picks drug up, he can show QR-Code in app or on printout (he got from doctor)
     \item pharmacy can access "Telematikinfrastruktur" to validate prescription
     \item pharmacy gives drug if validated
\end{enumerate}
~\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Access to prescription. Self-service: Digital management of prescriptions (prescription-tokens) inside app
     \item Service: Receiving drug for valid prescription. Self-service: Digital delivery of prescription (prescription-token)
           to pharmacy and digital instruction of delivery of drug
\end{itemize}

@@

\chapter{CSS Providers}

>>>>

DCSS is made available through DCSS providers. They can consist of websites and applications developed in self-work or be 
services provided by separate companies.

@@

\chapter{Objective}

@@

The objective of this bachelor thesis is to improve the capability of enterprises and organizations to integrate DCSS providers.
The thesis explains the basis of what DCSS and its providers are, which relevant scenarios exist and how DCSS providers can help
in the digital transformation.

@@

Based on scenarios resulting from governmental regulations (due to their current relevance), an integration architecture is presented, which describes
their integration. It provides information on which type of systems and data objects an existing
architecture requires. It models how CSS providers and system architectures can communicate -
deliver data and instructions. And it shows how, with fast development and deployment speed, integration can be applied to
heterogeneous system architectures, be non-invasive and reliable.

@@

Governments see digitalization as a chance for improvements in many important social and economical areas\todo{references}. The process of digitalization can in
some cases be described as reinventing existing solutions for usability with computers. One of the goals is to make solutions more easily accessible for users and as a 
method, provide digital self-service. Governmental regulations relating to digitalization therefore often encourage or demand enterprises and organizations to 
provide DCSS.

@@

\chapter{DCSS Providers}

@@

\subsection{Training Promotion (BAfï¿½G)}
\textbf{Available Resources}
\begin{itemize}
     \item Data Schema
     \item Process Diagram
     \item Click-Dummy
\end{itemize}

@@

The DSGVO influences DCSS by regulating how digitally collected personal information (which is common in DCSS) has to be managed. This means, DCSS providers have to 
keep this regulation in mind when designing their solutions. It has implications on integration in that DSGVO compliance requires special management of data, 
which an integration system has to make possible (DCSS providers use it).

It has to be analyzed in regard to:
\begin{enumerate}
     \item Which parts of the regulation describe requirements for features of DCSS providers
     \item Which parts of the regulation describe requirements for integrations
\end{enumerate}

@@

\subsection{e-Prescription}
Reference can be found in the "Ärzteblatt" \cite{Ärzteblatt}.
\\\\
The user can have the right to manage his prescriptions via an App. Doctors give digital prescriptions to users app,
which can digitally be used in pharmacies also without physically being there.
\\\\
Regulation: "Gesetz für mehr Sicherheit in der Arzneimittelversorgung (GSAV)"
\\\\
e-Prescription processes \cite{gematik-e-rezept}
\begin{enumerate}
     \item Doctor creates digital prescription if he has access to "Telematikinfrastruktur" and "Heilberufausweis"
     \item Prescription is saved on "Telematikinfrastruktur"
     \item Doctor displays a QR-Code (prescription-token)
     \item Patient can receive QR-Code in App (or get a printout)
     \item Patient can check availability of drug in pharmacies via the app
     \item Patient can "apply" the prescription to a pharmacy via the app
     \item prescription is now irrevocably bound to the pharmacy and gets reserved
     \item pharmacy can use prescription-token (in QR-Code) to access prescription in "Telematikinfrastruktur"
     \item pharmacy notifies patient if or when the drug is available
     \item drug can be picked up by patient or be delivered
     \item If user picks drug up, he can show QR-Code in app or on printout (he got from doctor)
     \item pharmacy can access "Telematikinfrastruktur" to validate prescription
     \item pharmacy gives drug if validated
\end{enumerate}
~\\
Enterprises are "allowed" to provide the IT-Structure behind the App, meaning the communication with a pharmacy and the receiving of prescription-tokens.
\\\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Access to prescription. Self-service: Digital management of prescriptions (prescription-tokens) inside app
     \item Service: Receiving drug for valid prescription. Self-service: Digital delivery of prescription (prescription-token)
           to pharmacy and digital instruction of delivery of drug
\end{itemize}

\section{PSD2}

The regulation is about how digital payment self-service providers have to function. This includes their communication / integration\cite{psd2Summary}.
\\\\
Full law at \cite{psd2}
\\\\
Regulation: "Payment Services Directive 2" (PSD2) (European law)
\\\\
What are services and what are self-services in this scenario:
\begin{itemize}
     \item Service: Payments and transfers. Self-service: Payment services are DCSS providers and offer digital execution of payments and transfers
\end{itemize}
~\\
The regulation has to be analyzed regarding:
\begin{enumerate}
     \item Which parts of the regulation describe required features of the self-service provider
     \item Which parts of the regulation describe requirements for integration
\end{enumerate}

@@
